A geometric approach to linear and quadratic Chabauty

### 2020-01-17 MS.tex
Cleaned up section smooth points

As $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$. That means that the blowup $\Tilde{X}_x \to X$ is the pullback of the blowup $\Tilde{\A}^d_{\Z_p,a} \to \A^d$. Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e. $\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d/p}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_p}]$ given by $x_i \mapsto p\Tilde{x_i}$. That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$). If furthermore $f$ is locally of finite type, then by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
\[
\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f + (p^n) \in \Z/p^n\Z[\Tilde{x_1},\dots,\tilde{X_d}] + (p^n) \right\}.
\]

>>>>

As $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$. That means that the blowup $\Tilde{X}_x \to X$ is the pullback of the blowup $\Tilde{\A}^d_{\Z_p,a} \to \A^d$. Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e. $\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d/p}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_p}]$ given by $x_i \mapsto p\Tilde{x_i}$. That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$). If furthermore $t$ is locally of finite type, then by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
\[
\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f + (p^n) \in \Z/p^n\Z[\Tilde{x_1},\dots,\tilde{X_d}] + (p^n) \right\}.
\]

Note that this construction is functorial, as in the following lemma:
\begin{lem}
Given two smooth schemes $X,Y$ over $\Z_p$, two $\F_p$-point $x\in X(\F_p), y\in Y(\F_p)$, there is a natural bijection between maps $f: Y \to X$ satisfying $f(y) = x$, and morphisms $\Tilde{Y}_y^p \to \Tilde{X}_Y^p$. 
\end{lem}
\begin{proof}

\end{proof}

Applying this lemma with $Y = \Spec \Z_p$ and $y$ the origin over $\F_p$, we get a natural bijection between $X(\Z_p)_x$ and $\Hom(O(\Tilde{x}_Y^p),\Z_p)$. As $\Z_p$ is $p$-adically complete, the map $t$ gives an isomorphism between $\Hom(O(\Tilde{x}_Y^p),\Z_p)$ and $\Hom(\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}},\Z_p) \cong \Z_p^d$.
